### 2017-12-08 manuscript.rmd
modified figures, fixed some code. New knit

```{r specimen_summary, results='asis', echo=FALSE, comment=NA, warning=FALSE}
specimen_data <- read.csv("supplementary_info/Specimen_data.csv")
names(specimen_data)<-c("New data","Species","ID","SRA Number", "Library ID", "Library type","Tissue","Sequencer", "Sequencing center", "Sample prep","Collected by","Collection date","Specimen id","Depth (m)","Geo loc name","Lat Lon","Voucher Type","Voucher location","Voucher Cat No.","Collection mode")

@@

#Mantle canal SIMMAP Setup
#mantle_data = cdata[which(!is.na(cdata$Mantle.Canal)),]
#mantle = mantle_data$Mantle.Canal
#names(mantle)=rownames(mantle_data)
#MantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(mantle))))
#make.simmap(MantleTree, mantle, nsim = 100, message=FALSE) -> mantle_sim
```

```{r sex, echo=F, message=F, warning=F, include=F}
par(ask=F)

#These are commented out to avoid outputting the figure on every knit (remove comment to generate)

#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 pdf("figures_raw/figure_5_raw_sex.pdf")
 densityMap(sex_sim)
 dev.off()
```

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
 plotTree(ultratree, lwd = 4)
 colors = c("black", "red")
 names(colors) = c("Absent", "Present")
 palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
 nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
 pdf("figures_raw/figure_5_raw_palpons.pdf")
 densityMap(palpons_sim)
 dev.off()
```

@@

Nectophores are non-reproductive propulsive medusae that codonophorans use for coordinated colony-level swimming (Fig. 2). Nectophores are also present within the gonodendra (reproductive structures) of the cystonects, and are thought to propel the gonodendra when they detach from the colony [@totton1965synopsis;@totton1960]. It is not clear whether the nectophores found within the siphosome of the cystonects is homologous to the nectophores borne on the nectosome of the codonophora. The nectosome is the region of the colony that develops from the nectosomal growth zone (Fig. 2B). Unlike the siphosomal growth zone, the nectosomal growth zone does not bud gastrozooids, but nectophores (and in the case of *Apolemia*, also palpons). The present tree, as well as the analyses of @Dunn:2005dy, are consistent with a single origin of the nectosome.

@@

@@

#####Stochastic Character maps
```{r tentilla, echo=F, message=F,warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim)
```

```{r tentilla2, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(tentilla_sim2)
```

```{r nectosome, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(nectosome_sim)
```

```{r mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
#densityMap(mantle_sim)
```

```{r nectosome_pos, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome. Cystonects were excluded as they do not have a nectosome."}
#SIMMAP NectoPos
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Dorsal", "Ventral")
# necto_pos_sim %>% plotSimmap(lwd = 4, add = T)
# nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
densityMap(necto_pos_sim)
```

#####Vertical Habitat Evolution
```{r median_cont, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV."}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

@@

#####Phylogenetic Signal

>>>>

```{r specimen_summary, results='asis', echo=FALSE, comment=NA, warning=FALSE}
specimen_data <- read.csv("supplementary_info/Supplementary_data_1_Specimen_data.csv")
names(specimen_data)<-c("New data","Species","ID","SRA Number", "Library ID", "Library type","Tissue","Sequencer", "Sequencing center", "Sample prep","Collected by","Collection date","Specimen id","Depth (m)","Geo loc name","Lat Lon","Voucher Type","Voucher location","Voucher Cat No.","Collection mode")

@@

#Descending mantle Canal SIMMAP Setup
desc_mantle_data = cdata[which(!is.na(cdata$Desc.Mantle.Canal)),]
desc_mantle = desc_mantle_data$Desc.Mantle.Canal
names(desc_mantle)=rownames(desc_mantle_data)
DescMantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(desc_mantle))))
make.simmap(DescMantleTree, desc_mantle, nsim = 100, message=FALSE) -> desc_mantle_sim

#Ascending Mantle canal SIMMAP Setup
asc_mantle_data = cdata[which(!is.na(cdata$Asc.Mantle.Canal)),]
asc_mantle = asc_mantle_data$Asc.Mantle.Canal
names(asc_mantle)=rownames(asc_mantle_data)
AscMantleTree =  drop.tip(ultratree, which(!(ultratree$tip.label %in% names(asc_mantle))))
make.simmap(AscMantleTree, asc_mantle, nsim = 100, message=FALSE) -> asc_mantle_sim
```

```{r sex, echo=F, message=F, warning=F, include=F}
par(ask=F)
#Simmap SEX
plotTree(ultratree, lwd = 4)
colors = c("black", "red")
names(colors) = c("Dioecious", "Monoecious")
sex_sim %>% plotSimmap(lwd = 4, add = T, colors=colors)
nodelabels(pie=(describe.simmap(sex_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
sex_obj <- densityMap(sex_sim, plot=FALSE)
sex_obj$cols[1:length(sex_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(sex_obj$cols))
 pdf("figures_raw/figure_5_raw_sex.pdf")
 plot(sex_obj)
 dev.off()
```

```{r palpons, echo=F, message=F, warning=F, include=F}
#Simmap PALPONS
 plotTree(ultratree, lwd = 4)
 colors = c("black", "red")
 names(colors) = c("Absent", "Present")
 palpons_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
 nodelabels(pie=(describe.simmap(palpons_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
 add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
palpons_obj <- densityMap(palpons_sim, plot=FALSE)
palpons_obj$cols[1:length(palpons_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(palpons_obj$cols))
 pdf("figures_raw/figure_5_raw_palpons.pdf")
 plot(palpons_obj)
 dev.off()
```

@@

Nectophores are non-reproductive propulsive medusae that codonophorans use for coordinated colony-level swimming (Fig. 2). Nectophores are also present within the gonodendra (reproductive structures) of the cystonects, and are thought to propel the gonodendra when they detach from the colony [@totton1965synopsis;@Totton1960]. It is not clear whether the nectophores found within the siphosome of the cystonects is homologous to the nectophores borne on the nectosome of the codonophora. The nectosome is the region of the colony that develops from the nectosomal growth zone (Fig. 2B). Unlike the siphosomal growth zone, the nectosomal growth zone does not bud gastrozooids, but nectophores (and in the case of *Apolemia*, also palpons). The present tree, as well as the analyses of @Dunn:2005dy, are consistent with a single origin of the nectosome.

@@

![Constrained topologies specified in SOWH testing. Test statistic and p-value for each tree estimated under constraint are given.](sowh/sowh_tests_supplemental_figure/sowh_tests_supplemental_figure.png)

@@

#####Stochastic Character maps
```{r tentilla, echo=F, message=F,warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla_obj <- densityMap(tentilla_sim,plot=FALSE)
tentilla_obj$cols[1:length(tentilla_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla_obj$cols))
plot(tentilla_obj)
```

```{r tentilla2, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included"}
#Simmap TENTILLA
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# tentilla_sim2 %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(tentilla_sim2, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
tentilla2_obj <- densityMap(tentilla_sim2, plot=FALSE)
tentilla2_obj$cols[1:length(tentilla2_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla2_obj$cols))
plot(tentilla2_obj)
```

```{r nectosome, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome"}
#Simmap NECTOSOME
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# nectosome_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(nectosome_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
nectosome_obj <- densityMap(nectosome_sim, plot=FALSE)
nectosome_obj$cols[1:length(nectosome_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(nectosome_obj$cols))
plot(nectosome_obj)
```

```{r desc_mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of a descending mantle canal in the nectophores. Cystonects and Athorybia were excluded as they do not have a nectosome. "}
#Simmap Descending Mantle Canal
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# desc_mantle_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(describe.simmap(desc_mantle_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
desc_mantle_obj <- densityMap(desc_mantle_sim, plot=FALSE)
desc_mantle_obj$cols[1:length(desc_mantle_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(desc_mantle_obj$cols))
plot(desc_mantle_obj)
```

```{r asc_mantle, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of an ascending mantle canal in the nectophores. Cystonects and Athorybia were excluded as they do not have a nectosome."}
#Simmap Ascending mantle canal
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Absent", "Present")
# asc_mantle_sim %>% plotSimmap(lwd = 4, add = T,colors=colors)
# nodelabels(pie=(ascribe.simmap(asc_mantle_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
asc_mantle_obj <- densityMap(asc_mantle_sim, plot=FALSE)
asc_mantle_obj$cols[1:length(asc_mantle_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(asc_mantle_obj$cols))
plot(asc_mantle_obj)
```

```{r nectosome_pos, echo=F, message=F, warning=F,  fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome. Cystonects were excluded as they do not have a nectosome."}
#SIMMAP NectoPos
# plotTree(ultratree, lwd = 4)
# colors = c("black", "red")
# names(colors) = c("Dorsal", "Ventral")
# necto_pos_sim %>% plotSimmap(lwd = 4, add = T)
# nodelabels(pie=(describe.simmap(necto_pos_sim, plot=F)$ace) ,piecol=colors,cex=0.35)
# add.simmap.legend(colors = colors, x=0.6*par()$usr[1],y=0.3*par()$usr[4],prompt=FALSE)
necto_pos_obj <- densityMap(necto_pos_sim, plot=FALSE)
necto_pos_obj$cols[1:length(necto_pos_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(necto_pos_obj$cols))
plot(necto_pos_obj)
```

```{r median_cont, echo=F, message=F, warning=F, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV."}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

@@
